Age-related changes in plant growth and traits

### 2015-04-23 Accessory_results.rmd
small work on Accessory tissue results

@@

plot_yvar_vs_xvar(data, yvar, xvar,
                  xlab=xvar, ylab=yvar)
mod <- lm(asin(sqrt(PerPropagule)) ~ species, data)
summary(mod)
```

@@

#Do individual species decrease accessory costs as they increase in size, age or RA?
First looking at size:
PerAcc is arcsine transformed, size is log transformed
COER, HATE, and PILI show a significant decrease in accessory costs with increasing size (p<0.05)
GRSP, PILI shows a marginally significant decrease in accessory costs with increasing size (0.05<p<0.10)
PEPU shows a marginally significant INCREASE in accessory costs with increasing size (0.05<p<0.10)
```{r, echo=FALSE,results='hide', message=FALSE}
yvar <- "PerAcc"
xvar <- "FinalWeight"

@@

With respect to age:
PerAcc is arcsine transformed, age is log transformed
BOLE, COER, HATE, HEPU, PELA show a significant decrease in accessory costs with increasing age (p<0.05)
EPMI, GRSP, HATE shows a marginally significant decrease in accessory costs with increasing age (0.05<p<0.10)
PUTU shows a sig INCREASE in accessory costs with increasing age
```{r, echo=FALSE,results='hide', message=FALSE}
yvar <- "PerAcc"
xvar <- "age"

@@

#Next considering if the amount of energy spent on aborted buds shifts with age, size, RA
First looking at size:
PerPrePol_A is arcsine transformed, size is log transformed
GRSP, HATE, HEPU, PUTU show a significant decrease in aborted buds with increasing size (p<0.05)
```{r, echo=FALSE,results='hide', message=FALSE}
yvar <- "PerPrePol_A"
xvar <- "FinalWeight"

@@

With respect to RA:
both RA and PerPrePol_All are arcsine transformed
BAER, BOLE, COER, GRSP, HATE, HEPU, LEES, PELA, PEPU show a significant decrease in total pre-pollination costs with increasing RA (p<0.05)
```{r, echo=FALSE,results='hide', message=FALSE}
yvar <- "PerPrePol_All"
xvar <- "RA"

@@

With respect to Reproductive Investment:
PerPrePol_All is arcsine transformed, ReproInv is log transformed
COER, GRBU, GRSP, HATE, PEPU, PHPH, PILI show a significant decrease in total pre-pollination costs with increasing reproductive investment (p<0.05)
LEES and PELA show a marginally significant decrease in total pre-pollination costs with increasing reproductive investment (0.05<p<0.10)
```{r, echo=FALSE,results='hide', message=FALSE}
yvar <- "PerPrePol_All"
xvar <- "ReproInv"

>>>>

```{r, echo=FALSE,results='hide', message=FALSE}
library(remake)
create_bindings()

source("scripts/summary_dataframes.R")
```

@@

plot_yvar_vs_xvar(data, yvar, xvar)
mod <- lm(asin(sqrt(PerPropagule)) ~ species, data)
summary(mod)
```

@@

#Do individual species decrease accessory costs as they increase in size, age or RA?
First looking at size:
PerAcc is arcsine transformed, size is log transformed
COER, HATE, and PILI show a significant decrease in accessory costs with increasing size (p<0.05)
GRSP shows a marginally significant decrease in accessory costs with increasing size (0.05<p<0.10)
PEPU shows a marginally significant INCREASE in accessory costs with increasing size (0.05<p<0.10)
```{r, echo=FALSE,results='hide', message=FALSE}
yvar <- "PerAcc"
xvar <- "FinalWeight"

@@

With respect to age:
PerAcc is arcsine transformed, age is log transformed
BOLE, COER, GRSP, HATE, HEPU, PELA show a significant decrease in accessory costs with increasing age (p<0.05)
EPMI, GRBU shows a marginally significant decrease in accessory costs with increasing age (0.05<p<0.10)
PUTU shows a sig INCREASE in accessory costs with increasing age
```{r, echo=FALSE,results='hide', message=FALSE}
yvar <- "PerAcc"
xvar <- "age"

@@

#Next considering if the amount of energy spent on aborted buds shifts with age, size, RA
First looking at size:
PerPrePol_A is arcsine transformed, size is log transformed
GRSP, HATE, HEPU show a significant decrease in aborted buds with increasing size (p<0.05)
PUTU shows a marginally significant decrease in accessory costs with increasing RA (p ~ 0.10)
```{r, echo=FALSE,results='hide', message=FALSE}
yvar <- "PerPrePol_A"
xvar <- "FinalWeight"

@@

With respect to RA:
both RA and PerPrePol_All are arcsine transformed
BAER, BOLE, COER, GRSP, HATE, HEPU, LEES, PEPU show a significant decrease in total pre-pollination costs with increasing RA (p<0.05)
PELA shows a marginally significant decrease in total pre-pollination costs with increasing RA (0.05<p<0.10)
```{r, echo=FALSE,results='hide', message=FALSE}
yvar <- "PerPrePol_All"
xvar <- "RA"

@@

With respect to Reproductive Investment:
PerPrePol_All is arcsine transformed, ReproInv is log transformed
COER, GRBU, GRSP, HATE, PEPU, PHPH, PILI show a significant decrease in total pre-pollination costs with increasing reproductive investment (p<0.05)
LEES shows a marginally significant decrease in total pre-pollination costs with increasing reproductive investment (0.05<p<0.10)
```{r, echo=FALSE,results='hide', message=FALSE}
yvar <- "PerPrePol_All"
xvar <- "ReproInv"
